Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Non-Response Handled in Pollster
Non-Response Handled in Pollster

>>>>

To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and Internet use. This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.
